{\centering{\bfseries{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}}\par}
\addcontentsline{toc}{section}{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}

\begingroup
\renewcommand{\section}[2]{}
\begin{thebibliography}{}
	\bibitem{dadaya}
	Stroganov~Y.~V., Bogachenko~A.~E. Modeling Digital Document Flow
	Processes with Stochastic Timed Petri Nets~// 2024 6th International Youth
	Conference on Radio Electronics, Electrical and Power Engineering (REEPE).
	\newblock 2024.
	\newblock {С.}~1--5.
	
	\bibitem{reward2}
	Constantinescu~C., Trivedi~K. Dependability modeling of real-time
	systems using stochastic reward nets~// Microelectronics Reliability.
	\newblock 1995.
	\newblock Т.~35, {№}~6.
	\newblock {С.}~903--914.
	
	\bibitem{introspn}
	Bause~F., Kritzinger~P. Stochastic Petri Nets - An Introduction to the
	Theory.
	\newblock 2013.  11.
	\newblock {с.}~131.
	
	\bibitem{introspn2}
	Marsan~M.~A. Stochastic Petri nets: An elementary introduction~// Advances
	in Petri Nets 1989~/ {под ред. }Grzegorz~Rozenberg.
	\newblock Springer Berlin Heidelberg, 1990.
	\newblock {С.}~1--29.
	
	\bibitem{transient}
	Transient analysis of non-Markovian models using stochastic state classes~/
	András~H., Marco~P., Lorenzo~R. {[и~др.]}~// Performance
	Evaluation.
	\newblock 2012.
	\newblock Т.~69, {№}~7.
	\newblock {С.}~315--335.
	
	\bibitem{quantum-games}
	Piispanen~L., Pfaffhauser~M., Wootton~J. {[и~др.]}. Defining
	Quantum Games [Электронный ресурс].
	\newblock Режим доступа: \url{
		https://doi.org/10.48550/arXiv.2206.00089} (дата
	обращения: \today).
	
	\bibitem{quantum-theory}
	Discrete quantum theories~/ Andrew~J.~H., Gerardo~O., Amr~S.
	{[и~др.]}~// Journal of Physics A: Mathematical and Theoretical.
	\newblock 2014.
	\newblock Т.~47, {№}~11.
	\newblock {с.}~115--305.
	
	\bibitem{quantum-discrete}
	Gatti~L.~N., Lacalle~J. A model of discrete quantum computation~//
	Quantum Information Processing.
	\newblock 2018.
	\newblock Т.~17, {№}~8.
	\newblock {с.}~192.
	
	\bibitem{quantum-discrete2}
	Altafini~C., Ticozzi~F.. Modeling and Control of Quantum Systems:
	An Introduction~// IEEE Transactions on Automatic Control.
	\newblock 2012.
	\newblock Т.~57, {№}~8.
	\newblock {С.}~1898--1917.
	
	\bibitem{ps}
	Terence T. Phase Space [Электронный ресурс].
	\newblock Режим доступа:
	\url{https://www.math.ucla.edu/~tao/preprints/phase_space.pdf}
	(дата обращения: \today).
	
	\bibitem{quantum-discrete3}
	Kornyak~V.~V. Classical and quantum discrete dynamical systems~// Physics of Particles and Nuclei.
	\newblock 2013.  Jan.
	\newblock Т.~44, {№}~1.
	\newblock {С.}~47--91.
	
	\bibitem{5dchess}
	5D Chess With Multiverse Time Travel [Электронный ресурс].
	\newblock Режим доступа:
	\url{https://store.steampowered.com/app/1349230/5D_Chess_With_Multiverse_Time_Travel/}
	(дата обращения: \today).
	
	\bibitem{fide}
	FIDE laws of chess [Электронный ресурс].
	\newblock Режим доступа:
	\url{https://www.fide.com/FIDE/handbook/LawsOfChess.pdf} (дата обращения: \today).
	
	\bibitem{fen}
	Forsyth-Edwards Notation (FEN) [Электронный ресурс].
	\newblock Режим доступа:
	\url{https://www.chess.com/terms/fen-chess} (дата
	обращения: \today).
	
	\bibitem{oris}
	Oris Tool [Электронный ресурс].
	\newblock Режим доступа: \url{https://www.oris-tool.org/}
	(дата обращения: \today).
	
	\bibitem{prolog}
	SWI-Prolog [Электронный ресурс].
	\newblock Режим доступа: \url{https://www.swi-prolog.org/}
	(дата обращения: \today).
	
	\bibitem{prolog-clpfg}
	SWI-Prolog manual [Электронный ресурс].
	\newblock Режим доступа:
	\url{https://www.swi-prolog.org/man/clpfd.html} (дата
	обращения: \today).
	
	\bibitem{forward-transient}
	Choi~H.~K. Vidyadhar~G.~Trivedi K.~S. Transient analysis of
	deterministic and stochastic Petri nets~// Application and Theory of Petri
	Nets 1993.
	\newblock Springer, 1993.
	\newblock {С.}~166--185.
	
	\bibitem{regenerative-transient}
	German~R., Logothetis~D., Trivedi~K.~S. Transient analysis of Markov
	regenerative stochastic Petri nets: a comparison of approaches~// Proceedings
	6th International Workshop on Petri Nets and Performance Models.
	\newblock 1995.
	\newblock {С.}~103--112.
	
	\bibitem{reward}
	Miklos~T., ~Andras~P. Performance analysis of Markov regenerative reward
	models~// Performance Evaluation.
	\newblock 1996.
	\newblock Т. 27-28.
	\newblock {С.}~1--18.
	
\end{thebibliography}
\endgroup
