\section*{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}
\addcontentsline{toc}{section}{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}

\begingroup
\renewcommand{\section}[2]{}
\begin{thebibliography}{}
	\bibitem{dadaya}
	Stroganov~Yuri~V., Bogachenko~Artyom~E. Modeling Digital Document Flow
	Processes with Stochastic Timed Petri Nets~// 2024 6th International Youth
	Conference on Radio Electronics, Electrical and Power Engineering (REEPE).
	\newblock 2024.
	\newblock {С.}~1--5.
	
	\bibitem{gost}
	ГОСТ 34.601-90 [Электронный ресурс].
	\newblock Режим доступа:
	\url{https://docs.cntd.ru/document/1200006921}, свободный (дата
	обращения: \today).
	
	\bibitem{ps}
	Terence Tao - Phase Space [Электронный ресурс].
	\newblock Режим доступа:
	\url{https://www.math.ucla.edu/~tao/preprints/phase_space.pdf},
	свободный (дата обращения: \today).
	
	\bibitem{fide}
	FIDE laws of chess [Электронный ресурс].
	\newblock Режим доступа:
	\url{https://www.fide.com/FIDE/handbook/LawsOfChess.pdf}, свободный
	(дата обращения: \today).
	
	\bibitem{fen}
	Forsyth-Edwards Notation (FEN) [Электронный ресурс].
	\newblock Режим доступа:
	\url{https://www.chess.com/terms/fen-chess}, свободный (дата
	обращения: \today).
	
	\bibitem{5dchess}
	5D Chess With Multiverse Time Travel [Электронный ресурс].
	\newblock Режим доступа:
	\url{https://store.steampowered.com/app/1349230/5D_Chess_With_Multiverse_Time_Travel/},
	свободный (дата обращения: \today).
	
	\bibitem{oris}
	Oris Tool [Электронный ресурс].
	\newblock Режим доступа: \url{https://www.oris-tool.org/},
	свободный (дата обращения: \today).
	
	\bibitem{prolog}
	SWI-Prolog [Электронный ресурс].
	\newblock Режим доступа: \url{https://www.swi-prolog.org/},
	свободный (дата обращения: \today).
	
	\bibitem{forward-transient}
	Choi~Hoon~Kulkarni Vidyadhar~G.~Trivedi Kishor~S. Transient analysis of
	deterministic and stochastic Petri nets~// Application and Theory of Petri
	Nets 1993.
	\newblock Springer, 1993.
	\newblock {С.}~166--185.
	
	\bibitem{regenerative-transient}
	German~R., Logothetis~D., Trivedi~K.S. Transient analysis of Markov
	regenerative stochastic Petri nets: a comparison of approaches~// Proceedings
	6th International Workshop on Petri Nets and Performance Models.
	\newblock 1995.
	\newblock {С.}~103--112.
	
	\bibitem{reward}
	Miklos~Telek~Andras~Pfening. Performance analysis of Markov regenerative reward
	models~// Performance Evaluation.
	\newblock 1996.
	\newblock Т. 27-28.
	\newblock {С.}~1--18.
	
\end{thebibliography}
\endgroup
